ext_risk_copula

### 2019-02-01 ext_risk_copula.Rmd
adding results : verhulst model

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

>>>>

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

```{r fig_abrewer_scl_0.8, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

model<-"austinbrewer"
scl<-0.8

numsims<-10000
numsteps<-25
numlocs<-5
s<-0.2
K<-50
p0<-K
rc<-1/(K*(1-exp(-s*K)))

rlist<-sort(c(0.002,0.004,0.006,0.008,0.01,0.015,rc,0.022,0.026))

abrewer_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store ext risk at dispersal d=0 for all r
colnames(abrewer_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

# plot for local dispersal in D matrix 
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    params<-c(r,K,s)
    ext_thrs<-p0/10
    s0<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    abrewer_extrisk_d0$risk_left_d0[i]<-s0$risk_left[1]
    abrewer_extrisk_d0$risk_right_d0[i]<-s0$risk_right[1]
    plot(s0$d_seq,s0$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
         xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s0$d_seq,s0$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(abrewer_extrisk_d0,paste(resloc,"abrewer_extrisk_d0.RDS",sep=""))

# plot for global dispersal in D matrix 
pdf(paste(resloc,"abrewer_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,K,s)
    ext_thrs<-p0/10
    s0<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s0$d_seq,s0$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
         xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s0$d_seq,s0$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# Plot ext_risk_d0
abrewer_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims

abrewer_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
abrewer_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims

pdf(paste(resloc,"abrewer_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025left,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025right,
       x1=abrewer_extrisk_d0$r,y1=abrewer_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.005,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.8) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_abrewer_r_vary_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model : K = 50, s = 0.2, rc = 0.02000091, scl=0.8) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_abrewer_r_vary_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Austin Brewer model with no dispersion : rc=0.02000091, scl=0.8); numlocs=5, numsteps=25, numsims=10000\label{fig_abrewer_risk_d0_scl_0.8}](./Results/austinbrewer_scl_0.8/abrewer_extrisk_d0.pdf){ width=40%, height=40% }

# Verhulst model :

```{r fig_verhulst_scl_2, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

model<-"verhulst"
scl<-2.5

numsims<-10000
numsteps<-25
numlocs<-5
p0<-1

rlist<-seq(from=0.2,to=1.8,by=0.2)

verhulst_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store ext risk at dispersal d=0 for all r
colnames(verhulst_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

# plot for local dispersal in D matrix 
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    ext_thrs<-p0/10
    s0<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=r,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    verhulst_extrisk_d0$risk_left_d0[i]<-s0$risk_left[1]
    verhulst_extrisk_d0$risk_right_d0[i]<-s0$risk_right[1]
    plot(s0$d_seq,s0$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
         xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s0$d_seq,s0$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(verhulst_extrisk_d0,paste(resloc,"verhulst_extrisk_d0.RDS",sep=""))

# plot for global dispersal in D matrix 
pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    ext_thrs<-p0/10
    s0<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=r,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s0$d_seq,s0$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),
         xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s0$d_seq,s0$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# Plot ext_risk_d0
verhulst_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=verhulst_extrisk_d0$risk_left_d0)/numsims
verhulst_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=verhulst_extrisk_d0$risk_left_d0)/numsims

verhulst_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=verhulst_extrisk_d0$risk_right_d0)/numsims
verhulst_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=verhulst_extrisk_d0$risk_right_d0)/numsims

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=2.5) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_verhulst_r_vary_scl_2.5}](./Results/verhulst_scl_2.5/verhulst_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model : rc = 1, scl=2.5) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_verhulst_r_vary_scl_2.5}](./Results/verhulst_scl_2.5/verhulst_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Verhulst model with no dispersion : rc = 1, scl=2.5); numlocs=5, numsteps=25, numsims=10000\label{fig_verhulst_risk_d0_scl_2.5}](./Results/verhulst_scl_2.5/verhulst_extrisk_d0.pdf){ width=40%, height=40% }
